How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-01 analysis/paper/paper.Rmd
likert plot

```{r}
library(tidyverse)
feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))

>>>>

```{r feedback-data-prep}
library(tidyverse)
feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))

# tidy the variable names
feedback <- 
  feedback %>% 
  rename_all(list(~str_squish(str_remove(., "\\d*:"))))

# extract yes/no questions
feedback_yn <- 
  feedback %>% 
  select(6, 8)

# extract likert-scale questions
feedback_likert <- 
  feedback %>% 
  select(seq(10, 19, 2)) %>% 
  mutate_all(as.factor)  %>% 
  mutate_all(tolower) %>% 
  as.data.frame()
```

```{r likert-plot}
mylevels <- c('strongly disagree', 'disagree', 'neutral', 'agree', 'strongly agree')

# Here we will recode each factor and explicitly set the levels
for(i in seq_along(feedback_likert)) {
	feedback_likert[,i] <- factor(feedback_likert[,i], levels=mylevels)
}

require(likert)
feedback_likert_out <- likert(feedback_likert)
plot(feedback_likert_out, wrap = 30)
```
